---
output:
  pdf_document: default
  html_document: default
  word_document: default
---
---
## CCAMP - Consumer Capital Asset Pricing Model

The goal is to create 10 regression models to identify beta values (risk)

Part of analysis is to create autocoreglama, investigate autocorrelation and apply reasonable Lag to solve autocorrelation problem. Autocorrelation means data correlated with itself over specific time

```{r}
library(Hmisc)
```

```{r}
CCAPM <- read.delim("Data/CCAPM.txt")
attach(CCAPM)
CCAPM[1:5,]
```

It shows financial instrument dependency of consumers, where r1 is a smaller company and their return of investment. Continuously, r2 is a bigger company with a lower possible return and risk and etc.


```{r}
acf(r1)
```

There is an autocorellation with 1, 7, 8, 12 months. Lag 8 (8 month) is not included since p value is to high and it does not required to solve autocorrelation problem

```{r}
m1 <- lm(r1 ~ cons + Lag(r1, 1) + Lag(r1, 7) + Lag(r1, 12))
summary(m1)
acf(residuals(m1))
```

By residuals autocoreglama, Lag problem is solved

```{r}
acf(r2)
```

Autocorrelation with 1, 8, 12 months

```{r}
m2 <- lm(r2 ~ cons + Lag(r2, 1) + Lag(r2, 8) + Lag(r2, 12))
summary(m2)
acf(residuals(m2))
```

```{r}
acf(r3)
```

Autocorrelation with 1, 8, 12 months

```{r}
m3 <- lm(r3 ~ cons + Lag(r3, 1) + Lag(r3, 8) + Lag(r3, 12))
summary(m3)
acf(residuals(m3))
```

Lags of more than 12 months are not very significant for given regression model

```{r}
acf(r4)
```

Autocorrelation with 1, 8, 12 months

```{r}
m4 <- lm(r4 ~ cons + Lag(r4, 1) + Lag(r4, 8) + Lag(r4, 12))
summary(m4)
acf(residuals(m4))
```

P value for Lag 12 is higher than 0.05, but lower than 0.10, so we will keep it since it is really important to solve autocorrelation case

```{r}
acf(r5)
```

Autocorrelation with 1, 8, 12 months

Important to mention that autocorrelation with 12 month influence is decreasing with every bigger company, lag with 12 month is decreasing

```{r}
m5 <- lm(r5 ~ cons + Lag(r5, 1) + Lag(r5, 8) + Lag(r5, 12))
summary(m5)
acf(residuals(m5))
```

```{r}
acf(r6)
```

Autocorrelation with 1, 8 months, 12 isnot significant anymore

```{r}
m6 <- lm(r6 ~ cons + Lag(r6, 1) + Lag(r6, 8))
summary(m6)
acf(residuals(m6))
```

```{r}
acf(r7)
```

Autocorrelation with 1, 8 months

```{r}
m7 <- lm(r7 ~ cons + Lag(r7, 1) + Lag(r7, 8))
summary(m7)
acf(residuals(m7))
```

Can be spotted that 5 month is very closed to be autocorrelated

```{r}
acf(r8)
```

Autocorrelation with only 8 month

```{r}
m8 <- lm(r8 ~ cons + Lag(r8, 8))
summary(m8)
acf(residuals(m8))
```

Lag 8 has 10.7% p-value, assumsing it is still significant, since it is around 10%

```{r}
acf(r9)
```

Autocorrelation with 8 month

```{r}
m9 <- lm(r9 ~ cons + Lag(r9, 8))
summary(m9)
acf(residuals(m9))
```

```{r}
acf(r10)
```

Autocorrelation with 5 month

```{r}
m10 <- lm(r10 ~ cons + Lag(r10, 5))
summary(m10)
acf(residuals(m10))
```

Based on summaries, beta (bigger risk, bigger return) values increased with a bigger company.

Bigger companies have less influence of 1 and 12 months for autocorrelation.